\begin{abstract}
	\RED{ Might need to redo this later}
	Allowing for further insight into I/O behavior and patterns has become increasingly important. I/O performance depends on a large number of components such as the applications access pattern, the computing system architecture, I/O libraries, file system, mode of access, data size, and the storage configuration and layout. Changes in these components can create high variations in I/O performance which could lead to many negative effects such as network congestion, poor scheduling and indicates a lack of understanding I/O variability. Not having the further insight into the I/O behavior makes it difficult to identify which of these components are affecting I/O variability and behavior.  
	%and most of the time strong correlations of I/O analyses across different applications are required to identify a possible solution. 
	This paper introduces a unique framework that provides low latency monitoring of I/O event data during run time. This is done through the implementation of a system-level infrastructure that continuously collects I/O application data from an existing I/O characterization tool. This allows insights into the I/O application behavior and the components affecting it through analyses and visualizations.
	The framework allows users to better understand throughput for system-specific behaviors, variations of I/O performance of similar applications across a system and identify correlations between I/O and system behavior. 
	%This paper demonstrates the implementation and design of this framework and how it can be used on various HPC applications.
\end{abstract}